Awareness of Stack Overflow Users to\\ Outdated and License-violating Code:\\ The Online Survey

### 2017-09-13 cloverflow_technical_report/cloverflow_survey_rn.tex
Latest update to RN.

Outdated third-party code and software licensing conflicts are ramifications by
reusing source code by copying and pasting (i.e.~code cloning). \cite{Xia2014}
show that a large number of open source systems reuse outdated third-party
libraries from popular open source projects. Using the outdated code give
detrimental effects to the software since they may introduce vulnerabilities. On
the other hand, \cite{German2009} found conflicts in software license between
the clones among different systems that come from the same source,~i.e.~clone
siblings.

The Internet encourages fast and easy way of sharing and copying code.
Developers nowadays do not only copy code from local software projects, but also
from online sources such as programming Q\&A website and online code
repositories. Stack Overflow is one of the most popular programming Q\&A
websites in the word. It has 7.6 million users, 14 million questions, 23 million
answers\footnote{Data as of 21 August 2017
	from~\url{https://stackexchange.com/sites}}, and more than 50 million developers
visiting each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}. Nevertheless, several code snippets on Stack
Overflow are found to be problematic. Many code snippets provided as solutions
are workarounds and occasionally contains defects or vulnerabilities.
\cite{Acar2016} performed a user study and found that Stack Overflow helps
developers to solve Android programming problems quicker than other resources
while, at the same time, offers less secure code than books or the official
Android documentation. Only 17\% of the Stack Overflow discussion threads the
participant visited during the study contain secure code snippets. They also
found that similar piece of API call copied from Stack Overflow by participants
in their study existed in a random sample of 200,000 Android apps from Google
Play. \cite{An2017} showed that 1,279 cloned snippets between 399 Android apps
and Stack Overflow potentially violate software licenses.

We are interested in studying the issues of outdated code and software license
violation cause by code snippets on Stack Overflow. Asking and answering
questions on Stack Overflow usually involve copying and pasting source code
snippets, either in a question or an answer. However, the copied snippets are
not regularly checked and occasionally not up-to-date with their originals. Some
snippets are copied from an open source system with stricter software license
than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Before
this study, we performed an preliminary study using code clone detection tools
to locate cloned code snippets in accepted answers. We found that many snippets
were copied from open source projects. Some cloned snippets are outdated and
possibly violating the original software license. In either case, these snippets
are potentially harmful for reuse. To accompany the findings and to gain
insights into the cause of this problem, we resort to a qualitative study using
an online survey of Stack Overflow developers who 1) answer programming
questions with code snippets and 2) reuse code snippets from Stack Overflow
answers.

@@

\section{Research Questions}
In this study, we would like to answer the following
research questions:

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
%	\item \textbf{RQ4(Awareness of Stack Overflow visitors to outdated code):} \textit{Are Stack Overflow visitors aware of outdated code on Stack Overflow?}
%	\item \textbf{RQ5 (Awareness of Stack Overflow visitors to software licensing conflicts):} \textit{Are Stack Overflow visitors aware of of software licensing conflicts caused by reusing code snippets from Stack Overflow?}
\end{enumerate}

\section{Research Methodology}
The study is performed using an online survey. We designed the survey using
Google Forms by following the principles of survey research
by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. 
%We created two versions of the
%survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. 
The survey is completely anonymous and the participants could decide to leave at
any time. It does not collect any sensitive personal information from the
participants and were approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at UCL.  The complete version of
the survey can be found in the Appendix~\ref{appendixA}.

\subsection{The Survey Design}
The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions were mandatory while the other 9 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, experience of
answering Stack Overflow questions, sources of the Stack Overflow snippets,
concerns of copying code snippets to Stack Overflow, problems from code 
snippets on Stack Overflow, fixing outdated code, and additional feedbacks.

\subsection{Participants}

\begin{table}
	\centering
	\caption{The Stack Overflow answerer taken the surveys}
	\label{tab:answerers}
	\begin{tabular}{lrrrr}
		\toprule
		Target group & Reputation & Sent emails & Answers & Rate \\
		\midrule
		Answerer Group 1 & 963,731--7,674 & 300 & 113 & 38\% \\
		Answerer Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
		\midrule
		Total & -- & 607 & 198 & 33\% \\
		\bottomrule
	\end{tabular}
\end{table}

@@

%\subsection{The Visitor Survey}
%
%The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
%questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
%questions. The first four questions were mandatory while the other 12 questions
%were shown to the participants based on their previous answers. The survey collects
%information of the participant's software development experience, importance of
%Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
%Stack Overflow snippets, licensing of code on Stack Overflow, and additional
%feedbacks.
%
%\begin{table}
%	\centering
%	\caption{The Stack Overflow visitors taken the survey}
%	\label{tab:visitors}
%	\begin{tabular}{lr}
%		\toprule
%		Invitation channels & Answers \\
%		\midrule
%		Chaiyong's Facebook post & 47 \\
%		Blognone.com & 32 \\
%		University of Molise & 6 \\
%		comp.lang.java.programmer & 3 \\
%		Software Engineering Facebook page & 1 \\
%		\midrule
%		Total & 89 \\
%		\bottomrule
%	\end{tabular}
%\end{table}
%
%The participants for this survey were invited to take the survey via five
%channels. The first channel is via the first author's Facebook post where the
%first author invited friends who are software developers and have experience of
%copying code snippets from Stack Overflow to take the survey. The second channel
%is a popular Thai technology news and media community called blognone.com which
%attracts a high number of software developers. The first author posted an
%invitation to the visitor survey in a discussion forum. The third channel
%collects answers from University of Molise which is the third author's
%workplace. The last two channels are from a comp.lang.java.programmer Google
%groups and Software Engineering Facebook page. The survey was open for
%participation for a month, from 25 July 2017 to 25 August 2017, before we
%collected and analysed the responses. The number of participants taken the
%survey are shown in Table~\ref{tab:visitors}.

@@

%\subsection{Answerer Responses}
We received 113 answers (38\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

The participants are active users and regularly answer questions on Stack Overflow (see Figure~\ref{fig:survey_answer_frequency}). Ninety two (81\%) and fifty one (61\%) of answerers from Group 1 and Group 2  answer questions at least once a week.

More than half of the answerers very frequently (81--100\% of the time) or frequently (61--80\% of the time) include code snippets in their answers. To break down into two groups as depicted in Figure~\ref{fig:survey_answer_frequency_with_code},
Group 1 very frequently (48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise, Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).

@@

To answer this research question, we ask the participants of the original
sources for their code examples. We provided six options (allowing more than one answer)
including \textit{I copied them from my own personal projects}, \textit{I copied
	them from my company's projects}, \textit{I copied them from open source
	projects}, \textit{I wrote the new code from scratch}, \textit{I copied the code
	from the question and modify it for the answer}, and \textit{Others}. From the
answers (Figure~\ref{fig:survey_snippet_source}), Stack Overflow answerers
in Group 1 mainly write new code from scratch (112) or copy from the code snippets in question
and modify it for the answer (108), followed by from their personal
projects (101), open source projects (73), other sources (57), and company projects (46). 
For Group 2, the most selected option is also writing code from scratch (83), followed by copying
from personal projects and modifying from the question (77), copying from open source projects (56),
copying from other sources (40), and copying from company projects (31).

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.5cm]{0.98\textwidth}{%
		\textit{For RQ 1, we found almost every answerer writes the new code from scratch or modifies from the code in question most of the time. Other less popular choices include copying code from their personal projects, and open source projects. Company projects are the least popular choice.}
	}%
}
\vspace{0.5cm}

@@

Roughly half of the top answerers on Stack Overflow
are aware of outdated code in their answers. We found that 72.3\% of Stack Overflow answerers in Group 1 have been notified of
outdated code in at least one of their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 57.1\% in
Group 2.

@@

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1.2cm]{0.98\textwidth}{%
		\textit{For RQ 2, we found that the majority of Stack Overflow answerers are aware of outdated code in their answers and fixed them. Nonetheless, there are approximately 19\% of the answerers who rarely or never fix their outdated code.}
	}%
}
\vspace{0.5cm}

@@

As shown in Figure~\ref{fig:survey_license_known}, more than half of the
answerers in both groups (63.4\% and 61.9\% respectively) are aware that Stack
Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA
3.0) to content in the posts, including code snippets, while the rest of 36.6\%
and 38.1\% are not.

@@

In addition, we found that almost every answerer in both groups (98\% and
99\% respectively) do not include license statement in their code snippets
(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
gave more information regarding this question in the open comment question and
we summarised them into three groups as follows. First, some answerers chose to post only their
own code or code that was adapted from the question. They are hence
automatically subjected to CC BY-SA 3.0. Second, they copied code from company
or open source projects that they knew were permitted to be publicly
distributed. Third, some answerers believe that code snippets in their answers
are too small to claim any intellectual property on them and fall under fair
use~\citep{fairuse}.

@@

We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0. As shown in Figure~\ref{fig:survey_license_check}, 67.9\% -- 69\% of answerers from both groups did not perform the checking. There are only approximately 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.

@@

In addition, we invited the answerers to give comments regarding their concerns when answering Stack Overflow (SO) with code snippets. Some interesting comments are selected and discussed belwo. The full set of answers can be found in the Appendix~\ref{appendixC}.

\begin{itemize}[label={}]
	\itemsep1em
	\item Comment 1: The answerer addresses a concern of reusing the code snippet without understanding. Moreover, he or she discusses a ramification of low-quality snippets or outdated code containing security issues.

@@

	\item Comment 2: The answerer suggests that a guidance from Stack Overflow regarding software license will be beneficial.

@@

	\item Comment 3: The answerer addresses a concern of code understanding.

@@

	\item Comment 4: The answerer discusses a problem from outdated code and his/her solution.

@@

%\subsection{Visitor Responses}
%
%To answer RQ4 and RQ5, we ask Stack Overflow visitors about their experiences of outdated code and their awareness to software license of Stack Overflow code snippets. We received 89 answers from 5 groups of Stack Overflow visitors. The combined results and discussions are presented below.
%
%\subsubsection*{RQ4: Are Stack Overflow visitors aware of outdated code on Stack Overflow?}
%
%We asked the visitors whether they have any problem from reusing Stack Overflow code snippets and how often did the problems occur. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.5\linewidth]{survey_v_problems}
%	\caption{Number of visitors who experienced a problem from reusing Stack Overflow code snippets.}
%	\label{fig:survey_v_problems}
%\end{figure}
%
%
%\vspace{0.5cm}
%\noindent\fbox{%
%	\parbox[c][0.5cm]{0.98\textwidth}{%
%		\textit{For RQ4, }
%	}%
%}
%\vspace{0.5cm}
%
%\subsubsection*{RQ5: Are Stack Overflow visitors aware of software licensing of code snippets from Stack Overflow?}
%
%\vspace{0.5cm}
%\noindent\fbox{%
%	\parbox[c][0.5cm]{0.98\textwidth}{%
%		\textit{For RQ5, }
%	}%
%}
%\vspace{0.5cm}

@@

>>>>

%This study is interested in the problem of outdated code and software licensing
%violations caused by code cloning on Internet-based question and answer
%websites. 
Recent research shows that outdated third-party code and software
licensing conflicts are ramifications by reusing source code by copying and
pasting (i.e.~code cloning). \cite{Xia2014} report that a large number of open
source systems reuse outdated third-party libraries from popular open source
projects. Using the outdated code give detrimental effects to the software since
they may introduce vulnerabilities. On the other hand, \cite{German2009} found
that code cloning leads to conflicts in software license among different
systems.

The Internet encourages fast and easy code cloning by sharing and copying code
to and from online sources. Developers nowadays do not only clone code from local
software projects, but also from online sources such as programming Q\&A website
and online code repositories~\FIXME{Add citation}. Stack Overflow is one of the most popular
programming Q\&A websites in the word. It has 7.6 million users, 14 million
questions, 23 million answers\footnote{Data as of 21 August 2017
	from~\url{https://stackexchange.com/sites}}, and more than 50 million developers
visiting each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}. Nevertheless, several code snippets on Stack
Overflow are found to be problematic. Many code snippets provided as solutions
are workarounds and occasionally contains defects or vulnerabilities.
\cite{Acar2016} performed a user study and found that Stack Overflow helps
developers to solve Android programming problems quicker than other resources
while, at the same time, offers less secure code than books or the official
Android documentation. Only 17\% of the Stack Overflow discussion threads the
participant visited during the study contain secure code snippets. They also
found that similar piece of API call copied from Stack Overflow by participants
in their study existed in a random sample of 200,000 Android apps from Google
Play. \cite{An2017} showed that 1,279 cloned snippets between 399 Android apps
and Stack Overflow potentially violate software licenses.

\textbf{We are interested in studying the issues of outdated code and software license
violation cause by code snippets on Stack Overflow.} Asking and answering
questions on Stack Overflow usually involve copying and pasting source code
snippets, either in a question or an answer. However, the copied snippets are
not regularly checked and occasionally not up-to-date with their originals. Some
snippets are copied from an open source system with stricter software license
than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior to
this study, we performed an empirical study using code clone detection tools
to locate cloned code snippets in accepted answers. We found that many snippets
were copied from open source projects. Some cloned snippets are outdated and
possibly violating the original software license. In either case, these snippets
are potentially harmful for reuse. To accompany the findings and gain
insights into the cause of the problems, we resort to a qualitative study using
an online survey of Stack Overflow developers who 1) answer programming
questions with code snippets and 2) reuse code snippets from Stack Overflow
answers.

@@

\section{Research Questions}
In this study, we would like to answer seven research questions listed below. The first three questions will be
answered by the Stack Overflow answerer survey, while the last three questions will be answered by the
Stack Overflow visitor survey.

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ4 (Importance of Stack Overflow to developers):} \textit{Why developers choose to find programming solutions on Stack Overflow?}
	\item \textbf{RQ5 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
	\item \textbf{RQ6 (Awareness of Stack Overflow visitors to CC BY-SA 3.0 license):} \textit{Are Stack Overflow visitors aware of the the CC BY-SA 3.0 license enforced by Stack Overflow?}
	\item \textbf{RQ7 (Software licensing issues from Stack Overflow code snippets):} \textit{How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
\end{enumerate}

\section{Research Methodology}
The study is performed using an online survey. We designed the survey using
Google Forms by following the principles of survey research
by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. 
We created two versions of the
survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. 
The surveys are completely anonymous and the participants could decide to leave at
any time. It does not collect any sensitive personal information from the
participants and were approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at UCL.  The complete version of
the surveys can be found in the Appendix~\ref{appendixA}.

\subsection{The Answerer Survey}
The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions were mandatory while the other 9 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, experience of
answering Stack Overflow questions, sources of the Stack Overflow snippets,
concerns of copying code snippets to Stack Overflow, problems from code 
snippets on Stack Overflow, fixing outdated code, and additional feedbacks.

\begin{table}
	\centering
	\caption{The Stack Overflow answerer taken the surveys}
	\label{tab:answerers}
	\begin{tabular}{lrrrr}
		\toprule
		Target group & Reputation & Sent emails & Answers & Rate \\
		\midrule
		Answerer Group 1 & 963,731--7,674 & 300 & 117 & 39\% \\
		Answerer Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
		\midrule
		Total & -- & 607 & 202 & 33\% \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\subsection{The Visitor Survey}

The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
questions. The first four questions were mandatory while the other 12 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, importance of
Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
Stack Overflow snippets, licensing of code on Stack Overflow, and additional
feedbacks.

\begin{table}
	\centering
	\caption{The Stack Overflow visitors taken the survey}
	\label{tab:visitors}
	\begin{tabular}{lr}
		\toprule
		Invitation channels & Answers \\
		\midrule
		Social media (Facebook posts) & 47 \\
		Blognone.com & 32 \\
		University of Molise & 6 \\
		comp.lang.java.programmer & 3 \\
		Software Engineering Facebook page & 1 \\
		\midrule
		Total & 89 \\
		\bottomrule
	\end{tabular}
\end{table}

The participants for this survey were invited to take the survey via five
channels. The first channel is via the first author's Facebook post where the
first author invited friends who are software developers and have experience of
copying code snippets from Stack Overflow to take the survey. The second channel
is a popular Thai technology news and media community called blognone.com which
attracts a high number of software developers. The first author posted an
invitation to the visitor survey in a discussion forum. The third channel
collects answers from University of Molise which is the third author's
workplace. The last two channels are from a comp.lang.java.programmer Google
groups and Software Engineering Facebook page. The survey was open for
participation for a month, from 25 July 2017 to 25 August 2017, before we
collected and analysed the responses. The number of participants taken the
survey are shown in Table~\ref{tab:visitors}.

@@

\subsection{Answerer Responses}
We received 117 answers (39\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

@@

The participants are active users and regularly answer questions on Stack
Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty two (82\%) and
sixty (60\%) of answerers from Group 1 and Group 2  answer questions at
least once a week.
More than half of the answerers very frequently (81--100\% of the time) or
frequently (61--80\% of the time) include code snippets in their answers. To
break down into two groups as depicted in
Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
(48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).

@@

To answer this research question, we ask the participants for original
sources of their code examples. We provided six options (allowing more than one answer)
including \textit{I copied them from my own personal projects}, \textit{I copied
	them from my company's projects}, \textit{I copied them from open source
	projects}, \textit{I wrote the new code from scratch}, \textit{I copied the code
	from the question and modify it for the answer}, and \textit{Others}. The
answers are shown in Figure~\ref{fig:survey_snippet_source}. Participants
in Group 1 mainly write new code from scratch (116) or copy from the code snippets in question
and modify it for the answer (112), followed by from their personal
projects (105), open source projects (77), other sources (59), and company projects (48). 
For Group 2, the main source is also writing code from scratch (83), followed by copying
from personal projects and modifying from the question (77), copying from open source projects (56),
copying from other sources (40), and copying from company projects (31).

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2cm]{0.98\textwidth}{%
		\textit{For RQ 1, we found that answering questions by writing the new code from
			scratch is the most popular choice for Stack Overflow answerers followed by modifying from the code in question, or copying from personal projects. Other less
			popular choices include copying code from open
			source projects and from other sources. Copying code from company projects are the least popular choice.} }%
}
\vspace{0.5cm}

@@

Half of the top answerers on Stack Overflow
are aware of outdated code in their answers. We found that 71.6\% of Stack Overflow answerers in Group 1 have been notified of
outdated code in at least one of their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 57.1\% in
Group 2.

@@

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{For RQ 2, Stack Overflow answerers are aware of outdated code in their
			answers. Nonetheless, there are approximately 19\% of the answerers who rarely
			or never fix their outdated code.} }%
}
\vspace{0.5cm}

@@

As shown in Figure~\ref{fig:survey_license_known}, more than half of the
answerers in both groups (62.1\% and 61.9\% respectively) are aware that Stack
Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA
3.0) to content in the posts, including code snippets, while the rest of 37.9\%
and 38.1\% are not.

@@

Almost every answerer in both groups (98\% and 99\% respectively) does not
include license statement in their code snippets (numbers are shown in
Figure~\ref{fig:survey_license}). Some of the participants explain the reason in
the open comment question which we summarised into three groups as follows.
First, they choose to post only their own code or code that is adapted from the
question. The code is automatically subjected to Stack Overflow's CC BY-SA 3.0.
Second, they copy code from company or open source projects that they know are
permitted to be publicly distributed. Hence, no license statement is required.
Third, some answerers believe that code snippets in their answers are too small
to claim any intellectual property on them and fall under fair
use~\citep{fairuse}.

@@

We asked the answerers a follow-up question of how frequently they checked for a
conflict between software license of the code snippets they copied to their
answers and Stack Overflow's CC BY-SA 3.0. As shown in
Figure~\ref{fig:survey_license_check}, 69\% of answerers from both groups did
not perform the checking. There are only approximately 10\% of the answerers who
frequently checks for licensing conflicts when they copy code snippets to Stack
Overflow.

@@

In addition, we invited the answerers to give comments regarding their concerns
when answering Stack Overflow (SO) with code snippets. Some interesting comments
are selected and discussed below. The full set of answers can be found in the
Appendix~\ref{appendixC}.

\begin{itemize}[label={}] \itemsep1em \item Comment 1: The answerer addresses a
	concern of programmers reusing his/her code snippets without understanding them.
	Moreover, he or she discusses a ramification of low-quality snippets or outdated
	code containing security issues on Stack Overflow.

@@

	\item Comment 2: The answerer suggests that a guidance from Stack Overflow
	regarding software license of code snippets will be beneficial.

@@

	\item Comment 3: Similar to comment 1, the answerer addresses a concern of
reusing Stack Overflow code snippets without understanding.

@@

	\item Comment 4: The answerer discusses a problem from outdated Stack Overflow code snippets and
	his/her solution.

@@

\subsection{Visitor Responses}

To answer RQ4 and RQ5, we ask Stack Overflow visitors about their experiences of
outdated code and their awareness to software license of Stack Overflow code
snippets. We received 89 answers from 5 groups of Stack Overflow visitors. The
combined results and discussions are presented below.

\subsubsection*{General Information}

\begin{figure}
		\centering
		\includegraphics[width=0.5\linewidth]{survey_visitor_exp}
		\caption{Experience of the Stack Overflow visitors}
		\label{fig:survey_visitor_exp}
\end{figure}

As illustrated in Figure~\ref{fig:survey_visitor_exp}, 24 (27\%) and 21 (24\%)
of the participants in Stack Overflow visitor survey have over 10 years and 5-10
years of experience respectively. There are 19 participants (21\%) who have 3-5
years, 18 (20\%) who have 1-2 years, and 7 (8\%) participants who have less than a
year of programming experience.

\subsubsection*{RQ4: Why developers choose to find programming solutions on Stack Overflow?}

Similar to a study by~\cite{Acar2016}, we asked the participants to rank five options, without a tie, they will choose to
find programming solutions. The given five options include books, official documentations, Stack Overflow,
online repositories (e.g. GitHub), and others. The results are displayed in Figure~\ref{fig:survey_visitor_rankings-crop}.
We found that 47 out of 89 participants rank Stack Overflow as the 1st option to search for programming solutions, followed
by official documentation (33), online repositories (6), other resources (5), and books (1).

\begin{figure} \centering
	\includegraphics[width=.5\linewidth]{survey_visitor_rankings-crop} 
	\caption{Rankings of the resources developers use to solve programming problems}
	\label{fig:survey_visitor_rankings-crop} 
\end{figure}

We then shift the focus to only Stack Overflow. We ask the participants how frequently they reuse code snippets from answers on Stack Overflow.
According to the answers (see Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we found that 57 (64\%) participants actively reusing
code snippets from Stack Overflow. Eight participants (9\%) copy Stack Overflow
code everyday, 22 (25\%) do copying 3-6 times a week, 27 (30\%) do copying once or twice a week. There are 2 participants (2\%) who never
copy code from Stack Overflow.

\begin{figure} \centering
	\includegraphics[width=.5\linewidth]{survey_visitor_frequency_so_copy} 
	\caption{Frequency of copying code from Stack Overflow}
	\label{fig:survey_visitor_frequency_so_copy-crop} 
\end{figure}

To understand why the participants choose to copy code snippets from Stack
Overflow, we asked them to rate four reasons in Likert's scale (Strongly agree,
Agree, Undecided, Disagree, Strongly disagree). The four reasons include
\textit{They are easy to find by searching the web}, \textit{They solve problems
	similar to my problems with minimal changes}, \textit{The context of questions
	and answers helped me understand the code snippets better}, \textit{The voting
	mechanism and accepted answers helped filtering good code from bad code}. The
answers are depicted in Figure~\ref{fig:survey_visitor_why_copy_so}. More than 80\% of the
participants agree with all the four reasons.

\begin{figure} \centering
	\includegraphics[width=0.6\linewidth]{survey_visitor_why_copy_so} 
	\caption{Why did you copy and reuse code snippets from Stack Overflow?}
	\label{fig:survey_visitor_why_copy_so} 
\end{figure}

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1.5cm]{0.98\textwidth}{%
		\textit{For RQ4, Stack Overflow is ranked higher than official documentations, online repositories, and book as the resource to look for programming solutions. 
		Developers rely on Stack Overflow answers because they are easy to search for on the web. Moreover, 64\% of the participants reuse code snippets from
	Stack Overflow at least once a week.}
	}%
} \vspace{0.5cm}

\subsubsection*{RQ5: What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}

We asked the visitors whether they have any problem from reusing Stack Overflow
code snippets and how often did the problems occur.  Fifty seven (out of eighty seven) participants (see Figure~\ref{fig:survey_v_problems})
experienced a problem from reusing Stack Overflow snippets. Among the 57, there are 2 participants who found problems in more than 80\%
of the reused code snippets. Eight and sixteen faced problems from at least sixty and forty percent of the reused snippets.

%We did not specifically point out the problem 
%of outdated code but include it as one of the answers.

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_v_problems} 
	\caption{Number of visitors who experienced a problem from reusing Stack Overflow code snippets and the frequency.}
	\label{fig:survey_v_problems} 
\end{figure}

The problems from reusing Stack Overflow code snippets (illustrated in
Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions,the code
claims to solve the problem in the question while it does not,  (20 out of 57
$\approx$ 35\%); outdated solutions, i.e.~the code may work with the some older
versions of the library or API, but not the one they are using, (39 out of 57
$\approx$ 68\%); mismatched solutions, i.e.~the code solves the problem in the
question but it is not exactly the right solution for their problem, (40 out of
57 $\approx$ 70\%); and buggy code (1 out of 57 $\approx$ 2\%). Stack Overflow
visitors rarely report the problems back to the discussion threads (as can be
seen in Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32
participants who encounter problems of Stack Overflow snippets, 18 of them
(56\%) never report the problems. As shown in
Figure~\ref{fig:survey_visitor_how_report_problems}, the 14 participants who
reported the problems did so by writing a comment (10), down-voting the answer
(8), contacted the answerer (2), and posting the new and correct answer (2).

\begin{figure} \centering
	\includegraphics[width=.5\linewidth]{survey_visitor_problems} 
	\caption{Problems from reusing Stack Overflow code snippets}
	\label{fig:survey_visitor_problems} 
\end{figure}

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_visitor_freq_report_problems} 
	\caption{Frequency of Stack Overflow visitors reporting the problems back to Stack Overflow discussion threads}
	\label{fig:survey_visitor_freq_report_problems} 
\end{figure}

\begin{figure} \centering
	\includegraphics[width=.5\linewidth]{survey_visitor_how_report_problems} 
	\caption{Options that Stack Overflow visitors choose to report the problems from Stack Overflow snippets}
	\label{fig:survey_visitor_how_report_problems} 
\end{figure}

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][2cm]{0.98\textwidth}{%
		\textit{For RQ5, our survey results show that 57 out of 87 Stack Overflow
	visitors find a problem from reusing Stack Overflow code snippets. Ten
	participants experience the problems on more 80\% of the copied snippets and
	sixteen participants face the problems on 40--60\% of the reused code. The
	mostly found problem is a mismatched solution (40), followed by outdated
	solution (39), incorrect solution (20), and buggy code (1). Fifty-six percent
	of the participants never report the problems back to Stack Overflow.}}%
} \vspace{0.5cm}

\subsubsection*{RQ6: Are Stack Overflow visitors aware of the the CC BY-SA 3.0 license enforced by Stack Overflow?}

As depicted in Figure~\ref{fig:survey_visitor_cc_by-sa}, 74 out of 87 (85\%)
Stack Overflow visitors are not aware, at the time of copying the code, that
Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC
BY-SA 3.0) to content in the posts, including code snippets. As a consequence,
62\% of the visitors never give an attribution, which is required by CC BY-SA
3.0, to a Stack Overflow post they copied the code from (the complete statistics
can be found from Figure~\ref{fig:survey_visitor_attribution-sa}).

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_visitor_cc_by_sa} 
	\caption{Awareness of Stack Overflow visitor to CC BY-SA 3.0 license}
	\label{fig:survey_visitor_cc_by-sa} 
\end{figure}

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_visitor_attribution} 
	\caption{Attributions to Stack Overflow when reusing code snippets}
	\label{fig:survey_visitor_attribution-sa} 
\end{figure}

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{For RQ6, 85\% of the participants are not aware of Stack Overflow CC
	BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
	they copied the code snippets from.}}%
} \vspace{0.5cm}

\subsubsection*{RQ7: How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}

Figure~\ref{fig:survey_visitor_original_license} shows that 79\% (69) Stack
Overflow visitors who adopted code from Stack Overflow never check if the code
snippet originated from a different source (e.g. an open source project) with an
incompatible license to their projects.

Sixty-six percent of the participants never
check for licensing conflicts at all when reusing Stack Overflow code (see Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly,
possibly due to their fairly small size of code which might fall under fair use,
only 9\% of the participants experience legal issues by reusing code snippets on
Stack Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}).

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_visitor_original_license} 
	\caption{Checking for the original license of Stack Overflow code snippets}
	\label{fig:survey_visitor_original_license} 
\end{figure}

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_visitor_licensing_conflict_check} 
	\caption{Checking for licensing conflicts from reusing Stack Overflow snippets}
	\label{fig:survey_visitor_licensing_conflict_check} 
\end{figure}

\begin{figure} \centering
	\includegraphics[width=.4\linewidth]{survey_visitor_legal_issue} 
	\caption{Legal issues found from reusing Stack Overflow code snippets}
	\label{fig:survey_visitor_legal_issue} 
\end{figure}

\vspace{0.5cm} \noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{For RQ7, we found that 66\% of the visitors never check for software
	licensing conflicts between Stack Overflow code snippets and their projects.
	However, only 9\% of the participants encountered legal issues.}}%
} \vspace{0.5cm}

\section{Threats to Validity}

@@

We present the results from online surveys of Stack Overflow answerers and
visitors regarding their awareness and experience of answering and reusing code
snippets on Stack Overflow. We are interested in cloned code in Stack Overflow
answers. Two online surveys have been performed to find out \textit{where} are the code
snippets in Stack Overflow answers from and \textit{how} developers, in terms of both
Stack Overflow answerers and visitors, handle potential problem of outdated code
and software licensing conflicts.
